Human subjects and IRB approval

### 2025-04-15 notebook/results-crackdown.qmd
Switch from iconify to regular fontawesome

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~a~: Relationship with host government

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government

>>>>

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 2~a~: Relationship with host government

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 2~b~: Organization and relationship with host government

### 2025-04-15 notebook/results-funding.qmd
Switch from iconify to regular fontawesome

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~a~: Funding sources

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~b~: Relationship with host government and funding sources

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 4~c~: Relationship with host government, funding sources, and issue area

>>>>

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 4~a~: Funding sources

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 4~b~: Relationship with host government and funding sources

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 4~c~: Relationship with host government, funding sources, and issue area

### 2025-04-15 notebook/results-issue.qmd
Switch from iconify to regular fontawesome

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~a~: Issue area

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area

>>>>

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 3~a~: Issue area

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 3~b~: Relationship with host government and issue area

### 2025-04-15 notebook/results-practices.qmd
Clean up some notebook stuff
Switch from iconify to regular fontawesome

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~a~: Financial transparency

@@

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \right) \bigr]
\end{aligned}
$$
```{r h5a-calc-estimands}
h5a_mms <- preds_all %>% 
  group_by(feat_transp_short, .draw) %>% 
  summarize(avg = mean(.epred))

@@

::: {.callout-tip icon=false}
### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices

@@

::: {.callout-tip icon=false}
### {{< iconify fa6-solid flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~c~: Relationship with host government, organizational practices, and funding sources

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~d~: Relationship with host government, organizational practices, and issue area

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~e~: Relationship with host government, organizational practices, issue area, and funding sources

@@

::: {.callout-tip icon=false}
## {{< iconify fa6-solid flask-vial >}} Hypothesis 5~f~: Accountability

>>>>

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 5~a~: Financial transparency

@@

$$
\begin{aligned}
\theta =&\ \textbf{E}\bigl[ Y_i \mid \operatorname{do}\left( \text{Transparency} = \text{Yes} \right) \bigr]
\end{aligned}
$$

```{r h5a-calc-estimands}
h5a_mms <- preds_all %>% 
  group_by(feat_transp_short, .draw) %>% 
  summarize(avg = mean(.epred))

@@

::: {.callout-tip icon=false}
### {{< fa flask-vial >}} Hypothesis 5~b~: Relationship with host government, organizational practices

@@

::: {.callout-tip icon=false}
### {{< fa flask-vial >}} Hypothesis 5~b2~: Relationship with host government, organizational practices

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 5~c~: Relationship with host government, organizational practices, and funding sources

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 5~d~: Relationship with host government, organizational practices, and issue area

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 5~e~: Relationship with host government, organizational practices, issue area, and funding sources

@@

::: {.callout-tip icon=false}
## {{< fa flask-vial >}} Hypothesis 5~f~: Accountability

### 2025-04-15 notebook/survey-irb.qmd
Switch from iconify to regular fontawesome

<p class="text-center">
<a href="files/byu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; BYU IRB approval
</a> 
&nbsp;
<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; Christopher Newport IRB approval
</a>
&nbsp;
<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< iconify fa6-solid circle-check >}} &nbsp; Georgia State IRB approval
</a>
</p>

>>>>

<p class="text-center">
<a href="files/byu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< fa circle-check >}} &nbsp; BYU IRB approval
</a> 
&nbsp;
<a href="files/cnu-irb-approval.pdf" class="btn btn-md btn-success" target="_blank" role="button">
{{< fa circle-check >}} &nbsp; Christopher Newport IRB approval
</a>
&nbsp;
<a href="files/gsu-irb-approval.pdf" class="btn btn-success btn-md" target="_blank" role="button">
{{< fa circle-check >}} &nbsp; Georgia State IRB approval
</a>
</p>
